All Graphs Lead to Rome: Learning Geometric and Cycle Consistent Representations with Graph CNNs

### 2018-11-16 cvpr2019/main.tex
Fixed baselines - got something here

\begin{table*}
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
Method                                                    & L1 Loss           & L2 Loss           & BCE Loss \\
\hline\hline\hline
MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 & 0.107 $\pm$ 0.038 \\ \hline
MatchALS \cite{zhou2015multi} 100 Iterations              & 0.029 $\pm$ 0.023 & 0.008 $\pm$ 0.003 & 0.163 $\pm$ 0.094 \\ \hline 
MatchALS \cite{zhou2015multi} 400 Iterations              & 0.022 $\pm$ 0.022 & 0.008 $\pm$ 0.003 & 0.184 $\pm$ 0.102 \\ \hline 
PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.020 $\pm$ 0.019 & 0.007 $\pm$ 0.003 & 0.149 $\pm$ 0.108 \\ \hline 
PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.019 $\pm$ 0.017 & 0.007 $\pm$ 0.003 & 0.127 $\pm$ 0.108 \\ \hline 
PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.018 $\pm$ 0.016 & 0.007 $\pm$ 0.003 & 0.112 $\pm$ 0.105 \\ \hline 
Spectral                                                  & 0.023 $\pm$ 0.019 & 0.008 $\pm$ 0.005 & 0.113 $\pm$ 0.098 \\ \hline \hline
GNN, 12 Layers                                            & 0.027 $\pm$ 0.003 & 0.017 $\pm$ 0.003 & 0.701 $\pm$ 0.002 \\
\hline
\end{tabular}
\end{center}
% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02

\caption{
Results on Rome16K Correspondence graphs.
Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.
As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
Thus we test against ground truth correspondence graph adjacency matrices gotten from the bundle adjustment output.
}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
Method                                                    & $L_1$ Loss        & $L_2$ Loss        & BCE Loss \\

\hline\hline\hline
MatchALS \cite{zhou2015multi} 15 Iterations               & 0.052 $\pm$ 0.003 & 0.010 $\pm$ 0.002 & 0.107 $\pm$ 0.038 \\ \hline
MatchALS \cite{zhou2015multi} 100 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.220 $\pm$ 0.099 \\ \hline
% MatchALS \cite{zhou2015multi} 400 Iterations              & 0.007 $\pm$ 0.003 & 0.007 $\pm$ 0.003 & 0.225 $\pm$ 0.104 \\ \hline
PGDDS \cite{leonardos2016distributed} 15 Iterations       & 0.016 $\pm$ 0.002 & 0.006 $\pm$ 0.002 & 0.045 $\pm$ 0.037 \\ \hline
PGDDS \cite{leonardos2016distributed} 100 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.038 \\ \hline
% PGDDS \cite{leonardos2016distributed} 200 Iterations      & 0.013 $\pm$ 0.002 & 0.005 $\pm$ 0.002 & 0.039 $\pm$ 0.039 \\ \hline
Spectral                                                  & 0.054 $\pm$ 0.005 & 0.018 $\pm$ 0.004 & 0.114 $\pm$ 0.028 \\ \hline \hline
GNN, 12 Layers (ours)                                     & 0.027 $\pm$ 0.003 & 0.017 $\pm$ 0.003 & 0.701 $\pm$ 0.002 \\
\hline
\end{tabular}
\end{center}
% save-rome16kgeom0-normedskip2-loss-l1-geom-10-0 (028249) -> train : +3.1467e-02, test : +3.8864e-02, gt_l1 : +2.6321e-02, gt_l2 : +2.6321e-02

\caption{
Results on Rome16K Correspondence graphs, showing the mean and standard deviation of the $L_1$ and $L_2$.
Our method was not trained on ground truth corresopndences but using unsupervised methods and geometric side losses.
As our method gives soft labels, we use cannot use precision or recall as is standard in testing cycle consistency \cite{zhou2015multi}.
Thus we test against ground truth correspondence graph adjacency matrices gotten from the bundle adjustment output.
}
\end{table*}
